Visualizations for the manuscript

### 2022-04-06 metanalysis_visualization/manuscript_Figures.Rmd
remove duplicated label from markdown cell

```{r Interrupted time series by sex}
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))

>>>>

```{r Interrupted time series by sex bootstrap}
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))
